---
title: "TASK 3 K-Means Cluster"
output: github_document
---

# Objective

* So the objective of cluster or group datas which are similar in nature using K-Means cluster Algorithm .This Clustering comes under Uusuperwised Machine learning Models.



# Loading Dataset
* We will be usign *iris*  dataset, which is an in build dataset in R language. We will have a look at it column names and sampel of top 5 entries.

```{r}
names(iris)
```
```{r}
head(iris)
```


# Loading Necesasry Library

```{r message = FALSE,warning = FALSE}
library(Amelia)
library(factoextra)
library(NbClust)
require(cluster)
library(tidyverse)
```

# Check for Missing value.

```{r}
missmap(iris)
```

* We can see that there is no missing data. so we can proceed furture.


# Removing the dependent variable from the dataset.

* since our iris dataset consist of the dependent variable (Species), it should be removed before creating out cluster model.

```{r}
df <- iris[,-5]
```
* now with our independent variable removed, we will have to decide the number of clusted, for our dataset.

* SO inoreder to find the optimum Cluster value there are various methords we are using the classic *Elbow Methord* 

```{r}
fviz_nbclust(df, kmeans, method = "wss") +
  geom_vline(xintercept = 3, linetype = 2)+
  labs(subtitle = "Elbow method")
```


* From the above Graph we can clearly see that, number of clusters should be 3. where which the average within sum of squares are starting to reduce.

*Number of Clusters  = 3*

# Model Building

* We will be creating a K-Meand Cluster algorithm wiht out *iris* dataset.

```{r}
k_means <- kmeans(df, 3, nstart = 25)
``` 

* So We have created a model with 3 cluster, and now we want to see the number of entries comes into each cluster


```{r}
clust <- k_means$cluster
as.data.frame(clust) %>% 
  group_by(clust) %>%
  count()

```


We can see

  * 62 entries are clustered into cluster 1
  * 50 entries are clustered into cluster 2
  * 38 entries are clustered into cluster 3


# Visual Representation. 

* Now we will have a visual representation of each cluster


```{r}
fviz_cluster(k_means, df, geom = "point")
```

# Thank You
