---
title: "Regression - Supervised Machine Learning"
output: github_document
---

# Objective

  Objective is to create a model that will predict the Marks of a student given the number of Hours studied.
  
# Loading Necessary Library

```{r message = FALSE,warning = FALSE}
library(caTools)
library(ggplot2)
library(Metrics)
library(Amelia)
```

# Loading Data

```{r}

dataset <- read.csv('http://bit.ly/w-data')

```

# Checking Missing Value

```{r}
missmap(dataset,col = c('Yellow','black'))
```

We can see, our dataset has no missing value.



# Initial Analysis On Dataset


* First we will look how the data looks
```{r}
head(dataset,5)
```
* we will check the number of rows and columns in the dataset

```{r}
dim(dataset)
```

* Our Dataset consist of 25 rows with 2 columns.

We want to find how the Number of Hours studied impacts the Scores obtained by the student. We want to find the linear relation between Hours and Scores. So we can see that Score is our Dependent Variable and Scores is our Independent Variable. 



# Initial Discriptive Analysis

* First we will plot Hours Vs Score

```{r}
ggplot(dataset,aes(x= Hours,y= Scores)) +
  geom_point(color = "red") +
  ggtitle('Hours Vs Scores')
```

From the above scattern plot we can clearly see, there is a positive correlation, and the positive correlation can be found below.

```{r}
round(cor(dataset$Hours,dataset$Scores),2)
```

* We can see the correlation between Hour and Scores is *0.98* which is highly correlated, but we have to keep in mind *"Correlation does not imply causation"*

# Creating a model

* We will create a simple linear regression Model, to predict the Scores given the number of Hours, in our case it is 9.5 Hours.


## Spliting the Dataset

* Since our dataset consist of only 25 rows, we will create a model with entire dataset and we will predict it on the splitted dataset for more accuracy.

* The dataset is splited into two parts, Train and Test Dataset.

```{r}
sample <- sample.split(dataset,0.8)
train_dataset <- subset(dataset, sample == TRUE)
test_dataset <- subset(dataset,sample == FALSE)
```

* we have created Train and Test Dataset, Now we will create our model with train dataset

## Building Model

```{r}
regression_model <- lm(Scores~.,dataset)
summary(regression_model)
```

* We can see that Hours Variable is Highly significane in predicting the Scores, denoted by '***' and the R-Square value is 0.9446, indication that the model can explain 94% of varaince in the dataset.

* Our Simple Linear Equation will be *Score = 6.3512 + 9.1793(Hours)*

## Scatter Plot with regression line.

```{r}
ggplot(dataset,aes(x= Hours,y= Scores)) +
  geom_point(color = "red") +
  ggtitle('Hours Vs Scores') +
  geom_smooth(method = 'lm')
```




## Prediction on test dataset

```{r}
test_pred <- predict(regression_model,test_dataset)
```

* The Scores in test dataset is predicted and stored in test_pred.

## Model Performance

* Now we will measure how accuracy our model by MAE, Whynot RMSE ?, since RMSE area mostly preffered when there are outliers. In our case there were no outliers(From the above scatter plot.). The Lower the mae value, more the model performace.

```{r}
mae(test_dataset$Scores,test_pred)
```

*MAE = 4.91476*

# Final Prediction

* Now we have created a model, the last set is to predict marks for our given hours that is 9.25 hours

```{r}
predict(regression_model,data.frame(Hours = c(9.25)))
```

So, Our Model has predicted that a student, who studies for 9.25 hours will get a score of *92.909*, we will round it to 93.












